### 2019-02-19 sections/relatedwork.tex
added fixme to related work
small fixes and more fixmes

\paragraph{mTasks}
\fixme{Hier iets gezelligs over mTasks}
% Our work differs in three major ways.
% First, we make an explicit distinction between the host language and the task
% language, to emphasise their boundaries.
% Second, we make use of separate semantic functions for querying the current task
% value, determining the continuation after an input event, and producing a user
% interface.
% In iTasks and its aforementioned semantics, these are integrated into the
% \CL{Task} datatype.
% Third, our system does not have the notion of task stability.
% When desired, stability can be introduced by the programmer, but the system
% itself makes no use of it.
% We argue that this does not impact the expressiveness of our language.

@@

\paragraph{Workflow Nets}

Workflow Nets~(\WFN)\cite{journals/jcsc/Aalst98} allow for the modelling and analysis
of business processes. They are graphical in nature, and clearly display how
every component is related to each other. A downside of \WFN is that
they do not facilitate higher order constructs and that they are often not
directly executable.

\paragraph{YAWL}

This is not always the case however. A language based on \WFN that is
actually directly executable is \YAWL by \citet{DBLP:journals/is/AalstH05}.
It facilitates modelling and execution of
dynamic workflows, with support for \emph{and}, \emph{or} and \emph{xor} workflow patterns. As
mentioned, \YAWL programs consist of \WFN, and are therefore programmed
visually.

@@

@@

>>>>

\paragraph{mTasks}
\fixme{Hier iets gezelligs over mTasks}

% Our work differs in three major ways.
% First, we make an explicit distinction between the host language and the task
% language, to emphasise their boundaries.
% Second, we make use of separate semantic functions for querying the current task
% value, determining the continuation after an input event, and producing a user
% interface.
% In iTasks and its aforementioned semantics, these are integrated into the
% \CL{Task} datatype.
% Third, our system does not have the notion of task stability.
% When desired, stability can be introduced by the programmer, but the system
% itself makes no use of it.
% We argue that this does not impact the expressiveness of our language.

@@

\paragraph{Workflow Nets \& YAWL}

Workflow Nets~(\WFN) \cite{journals/jcsc/Aalst98} allow for the modelling and analysis of business processes.
They are graphical in nature, and clearly display how every component is related to each other.
A downside of \WFN is that they do not facilitate higher order constructs.
Also, they are often not directly executable.

A language based on \WFN that is actually directly executable is \YAWL by \citet{DBLP:journals/is/AalstH05}.
It facilitates modelling and execution of dynamic workflows, with support for \emph{and}, \emph{or} and \emph{xor} workflow patterns.
As mentioned, \YAWL programs consist of \WFN, and are therefore programmed visually.

@@

\fixme{Is this higher order? What combinators can be used? Other limitations?}

@@

\fixme{Write}
